---
title: "Homework_5"
author: "Arielle"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (tidyverse)
library (viridis)
library (gridExtra)
library (imputeTS)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

##Problem 1
```{r}
missing_values = function(x){
  if (is.numeric(x)) {
    (na_mean(x, option = "mean", maxgap = Inf)) }
    else if (is.character(x)) {
      (replace_na(x, "virginica"))}
}
```

```{r}
output = map(iris_with_missing, missing_values)
```

Created a function that replaced the missing NAs that were numeric with the mean non-missing values. Also in that same function replaced the NAs in the character with virginica.

##Problem 2
```{r}
df=
  tibble(observations = list.files(path = "data/", pattern = "csv", all.files = TRUE, full.names= TRUE)) %>% 
  mutate(df = map(observations, read_csv)) %>% 
  unnest()
```

```{r}
df1=
df %>% 
  janitor::clean_names() %>%
  mutate(
    observations= str_remove(observations, "data//"),
    observations = str_remove(observations, ".csv")) 
```


```{r}
df2 =
  df1%>% 
  mutate(observation = observations) %>% 
  separate(observations, into= c("arm", "subjectID"), sep = "_") %>%
  pivot_longer(
     week_1:week_8,
     names_prefix = "week_",
     names_to = "weeks",
     values_to = "value") 
```


```{r}
df2 %>%  
  group_by(subjectID, arm) %>% 
  ggplot(aes(x= weeks, y= value, group= observation, color = arm)) + geom_line() +labs(
    x = "Weeks",
    y = "Values",
    title= "Observations over 8 Week Period")
```

The experimental observations have an overall higher values than those in the controls.The experimentals increase over the eight week period, whereas the controls seem to slightly decreased over the same 8 week period. 

